CS287 Final Project Abstract

### 2019-03-27 abstract/abstract.tex
Changes to abstract

VQ-VAE has
been used \citep{kaiser2018fast} to speed up machine translation. VQ-VAE
achieves this by compressing sentences into shorter discrete representations,
which are then translated using a encoder--decoder framework (e.g. transformer).
The speedup is provided since the variational encoding and decoding parts are
parallelizable. We anticipate that VQ-VAE may also be helpful in low-resource
settings, since variational autoencoding is unsupervised. In particular, recent
advances in VQ-VAE has shown that it can style transfer audio into being spoken
by different
speakers, in a fully unsupervised manner \citep{van2017neural}. Speaker style
transfer is a task that
bears some similarities to translation, and we hope to
leverage these recent advances for low-resource machine translation.
% TODO: write up area

>>>>

VQ-VAE has been used \citep{kaiser2018fast} to speed up machine translation.
VQ-VAE achieves this by compressing sentences into shorter discrete
representations, which are then translated using a encoder--decoder framework
(e.g. transformer). The speedup is provided since the variational encoding and
decoding parts are parallelizable. We anticipate that VQ-VAE may also be helpful
in low-resource settings, since variational autoencoding is unsupervised. In
particular, recent advances in VQ-VAE has shown that it can style transfer audio
into being spoken by different speakers, in a fully unsupervised manner
\citep{van2017neural}. Speaker style transfer is a task that bears some
similarities to translation, and we hope to leverage these recent advances for
low-resource machine translation.% TODO: write up area
